---
title: "R Markdown and Leaflet"
author: "S.A.Aksyuk"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
---

```{r echo = F, message = F, warning = F}


# пакеты ----------------------------------------------------------------------
library('leaflet')


# настройки отображения отчёта ------------------------------------------------

# опции блоков кода ===========================================================
knitr::opts_chunk$set(echo = F, warning = F, message = F)

```


This map shows locations of The Russian Presidential Academy of National Economy and Public Administration buildings in Moscow, Russia. Zoom to expand south-west corner, where the main campus is situated.    

```{r}
fileURL <- 'https://raw.githubusercontent.com/aksyuk/Coursera_DDP/master/ranepa_logo.png'
ranepa.icon <- makeIcon(iconUrl = fileURL, 
                        iconWidth = 31*74/98,
                        iconHeight = 31,
                        iconAnchorX = 31*74/98 / 2,
                        iconAnchorY = 16)

fileURL <- 'https://raw.githubusercontent.com/aksyuk/Coursera_DDP/master/RANEPA_loc.csv'
df <- read.table(fileURL, header = T, as.is = T, 
                 sep = ';', dec = ',')
RANEPA.loc <- df[, c('lat', 'lng')]
ranepa.sites <- paste0("<a href='", df[, 'hyperlink'], "'>", 
                       df[, 'address_eng'], "</a></br><em>", 
                       df[, 'address_ru'], "</em>")

myMap <- RANEPA.loc %>% leaflet(width = 800, height = 800) %>% addTiles() %>% 
    addMarkers(icon = ranepa.icon, popup = ranepa.sites)
myMap

```

### R packages used  

1. Joe Cheng, Bhaskar Karambelkar and Yihui Xie (2017). leaflet: Create Interactive Web Maps with the JavaScript 'Leaflet' Library. R
  package version 1.1.0. https://CRAN.R-project.org/package=leaflet  

### Data sources  

1. RANEPA oficcial site. URL: [http://www.ranepa.ru/lyceum/infrastruktura/korpusa-akademii](http://www.ranepa.ru/lyceum/infrastruktura/korpusa-akademii)   
2. Map web-API from Yandex. URL: [https://yandex.ru/map-constructor/location-tool/](https://yandex.ru/map-constructor/location-tool/])  
